---
title: "Homework 5"
author: Jia-Ru Chung 
date: "November 9, 2017"
runtime: shiny 
output: html_document
---

```{r setup, include=F}
knitr::opts_chunk$set(echo = TRUE, tidy = TRUE)
library(shiny)
library(caret)
library(lattice)
library(ggplot2)
library(e1071)
```

**Note:**   
**GOOD NEWS** You do not need to knit your HW5, just submit the this .Rmd file!!

**BAD NEWS** You will also have to host your HW5 online, Q3 will explain how to do this!!

#### Max points = 100  

There are a few more details regarding RShiny and Rmarkdown, but rather than tell you about them, I am going to use this homework to force you to figure them out yourself.

It is possible to create an interactive Rmarkdown document, this is like a cross between an RShiny app and an Rmarkdown (A summary on how to do this is in your markdown-cheatsheet). I personally find this a little less complicated than making a full RShiny app. 

I have created an interactive Rmarkdown document that I would like you to recreate, click the [HW5_APP](https://tomall01.shinyapps.io/HW5_APP/) link to see it.

### Question 1 {40 pts}.

In the first section of **HW5_APP** there are several tabs, clicking on each tab will give a performance summary of our *glmnet*, *pls* and *pam* models in either **test** or **validation** data (the results of the models we trained in Lecture 10). Try to recreate these tabs and their contents using the *navbarPage()* and *tabPanel()* functions, I have included some code below to help you get started. The file *Lecture10Data.csv* contains the output (RESULTS.df) of our Lecture10 models. The code for the AsthmaApp.R in Lecture9 might be helpful to you, also the shiny-cheatsheet might be helpful. 

NOTE: You can test your app is working correctly by the clicking on **Run Document** in RStudio, or by typing **rmarkdown::run** into the console. Try it now to see what the app looks like, it will run!  
  
```{r echo=F}
## Modify the code below for inputs
RESULTS.df<-read.csv("Lecture10Data.csv")

# user interface

navbarPage(theme<-"Performance Summary",
            tabPanel('Test Data',
                     mainPanel(
                       tabsetPanel(
                         tabPanel("glmnet",verbatimTextOutput("GLM.TST")),
                         tabPanel("pls",verbatimTextOutput("PLS.TST")),
                         tabPanel("pam",verbatimTextOutput("PAM.TST"))))),
           tabPanel('Val Data',
                     mainPanel(
                       tabsetPanel(
                         tabPanel("glmnet",verbatimTextOutput("GLM.VAL")),
                         tabPanel("pls",verbatimTextOutput("PLS.VAL")),
                         tabPanel("pam",verbatimTextOutput("PAM.VAL"))))))

# Data Manipulation
PAM.VAL<-subset(RESULTS.df,TrainTestVal=='Val'&Method=="pam")
GLM.VAL<-subset(RESULTS.df,TrainTestVal=='Val'&Method=="glmnet")
PLS.VAL<-subset(RESULTS.df,TrainTestVal=='Val'&Method=="pls")

PAM.TST<-subset(RESULTS.df,TrainTestVal=='Test'&Method=="pam")
GLM.TST<-subset(RESULTS.df,TrainTestVal=='Test'&Method=="glmnet")
PLS.TST<-subset(RESULTS.df,TrainTestVal=='Test'&Method=="pls")

# server
output$GLM.VAL<-renderPrint({confusionMatrix(GLM.VAL$PredResp,GLM.VAL$Resp)})
output$PAM.VAL<-renderPrint({confusionMatrix(PAM.VAL$PredResp,PAM.VAL$Resp)})
output$PLS.VAL<-renderPrint({confusionMatrix(PLS.VAL$PredResp,PLS.VAL$Resp)})

output$GLM.TST<-renderPrint({confusionMatrix(GLM.TST$PredResp,GLM.TST$Resp)})
output$PAM.TST<-renderPrint({confusionMatrix(PAM.TST$PredResp,PAM.TST$Resp)})
output$PLS.TST<-renderPrint({confusionMatrix(PLS.TST$PredResp,PLS.TST$Resp)})


```  
\pagebreak 
 
### Question 2 {40 pts}.

The second section of **HW5_APP** contains a slider and a plot. The plot displays the Mean value for Symptoms.Past30D for each state, with the error bars representing the standard error of the mean. The slider controls which month (Jan=1, Dec=12) the data corresponds to. The dataset is the AsthmaChild.Ozone data from lecture9. See if you can recreate the slider and plot, I have provided some code to help you.
  
```{r echo=F}
sliderInput(inputId="month",
            label="Month: Jan=1, Dec=12",
            min = 1,
            max = 12,
            value=1,
            step=1)

x <- read.csv("AsthmaChild.Ozone.2006_2007.Sample.csv")
mainPanel(plotOutput("two"))

output$two<-renderPlot({
  dat <- subset(x,Month==as.numeric(input$month))
  data.mean = aggregate(dat$Symptoms.Past30D, by=list(dat$STATE), FUN=mean)
  names(data.mean) <- c("State","Mean")
  data.sd = aggregate(dat$Symptoms.Past30D, by=list(dat$STATE), FUN=sd)
  names(data.sd) <- c("State","SD")
  dat_final = merge(data.mean,data.sd, by = "State")
  print(dat_final)
  ggplot() + 
  geom_errorbarh(data=dat_final, mapping=aes(y=State,x = Mean, xmin=Mean-SD, xmax=Mean+SD), color="black") + 
  geom_point(data=dat_final, mapping=aes(y=State, x=Mean)) +
  coord_fixed(ratio = 5)
  
  #ggplot(dat,aes(x=Symptoms.Past30D,y=STATE)) + stat_summary(fun.x=mean_se)
  })
```    
\pagebreak    

   
  
### Question 3 {20 pts}.  

ShinyApps and interactive Rmarkdown can be hosted publically online, just like the HW5_APP I made for this homework. 

One such hosting service called [ShinyApps.oi](http://www.shinyapps.io/). I want you to visit ShinyApps website and follow the instructions to set up an account and then host your Homework 5 app online.

Once you have hosted your app, paste the url below, the closer your app is to mine, the more points you will get.

**Answer**  
<https://thetitan.shinyapps.io/archive/>
\pagebreak   


